---
title: "Homework 21"
output: html_notebook
---

# In this homework, I'll be working through chaoter 4 of "Getting Started With R"

## Setting up R and clearing its brain. 

```{r}
rm(list = ls())
library(ggplot2)
library(here)
library(dplyr)
```

## I will need some data, so I'll import a dataset to use for my charts. 

```{r}
Compensation <- read.csv(here("Data", "compensation.csv"))
```

##  This is how ggplot2 makes a basic scatterplot of a dataset. 

```{r}
ggplot(Compensation, aes(x = Root, y = Fruit)) + geom_point()
```

## In order to increase the size of points, additional information is entered within geom_point(). Here, I'll make the points larger. 

```{r}
ggplot(Compensation, aes(x = Root, y = Fruit)) + geom_point(size = 5)
```

## Labels of the X and Y axis can be modified using xlab() and ylab()

```{r}
ggplot(Compensation, aes(x = Root, y = Fruit)) + geom_point(size = 5) +
xlab("Root Biomass") +
ylab("Fruit Biomass")

# Remember to include + between commands, otherwise they won't occur together. 
```

## Color can also be adjusted using  "colour =", shwing the difference between grazed and ungrazed points. 



```{r}
ggplot(Compensation, aes(x = Root, y = Fruit, colour = Grazing)) + geom_point(size = 5) +
xlab("Root Biomass") +
ylab("Fruit Biomass")

```

## We can use R to make box-and-whisker plots. Using geom_boxplot() will work. 

```{r}
ggplot(Compensation, aes(x = Root, y = Fruit, colour = Grazing))  +
  geom_boxplot() +
xlab("Grazing Treatment") +
ylab("Fruit Producion")

#Remember to include +! Treatments are also written differently here. If kept the same, a box-and-whisker plot will appear on top of the scatterplot.Remove geom_point() for this!
```

## Histograms are another type of chart which R can be used to make. The code for this looks quite different, though. This initial one won't look too nice, but there are ways around that. 

```{r}
ggplot(Compensation, aes(x = Fruit)) +
  geom_histogram()
```

## Here's how we can produce a neater version with different code. 

```{r}
ggplot(Compensation, aes(x = Fruit)) +
  geom_histogram(bins = 10)
ggplot(Compensation, aes (x = Fruit)) +
  geom_histogram(binwidth = 15)
```

## Two histograms can be created at the same time! In this example, I'll make one for each grazing treatment.

```{r}
ggplot(Compensation, aes(x = Fruit)) +
  geom_histogram(binwidth = 15) +
facet_wrap(~Grazing)
```

## Plots can be saved! 

```{r}
ggsave("NewPlot.png")
```

