---
title: "R Notebook"
output: html_notebook
---
## Homework 19: Connecting Github to R and cleaning up Data 

# For this homework, I'll be working with R and github linked together. In R, I'll examine and tidy up some provided data. 

# First, I'll clear R's brain and set up necessary packages. 


```{r}
rm(list = ls())
library(dplyr)
library(here)
library(ggplot2)
```

# Next, I can import our dataset. 

```{r}
Leaves <- read.csv(here("Data", "Leaves.csv"), stringsAsFactors=TRUE)
```

# Using str(), I can get a better view of my data within R. This will show me what type of data I've imported, along with my variables. 

```{r}
str(Leaves)
```

# I'll begin by ensuring no columns have special characters or spaces in their names. 

```{r}
names(Leaves) <- c("Tree_num", "Species", "Leaf", "DBH_cm", "Petiole_length", "Total_length_cm", "Middle_lobe_length_cm", "Middle_lobe_width_cm", "Person")

# Removed additional periods and spaces present in column names. Underscores have been preserved between titles as R will not recognize spaces. c() allows me to change column titles--new titles will be listed in their intended order within c(). 
```

# levels() allows me to determine the number of factors within a variable. I needed to go back to when I imported Leaves.csv to add stringAsFactors, which converted 'Species' into a factor with 9 levels. Otherwsie, it gave me NULL for levels. 

```{r}
levels(Leaves$Species)
# As species data is Chr data, there are no levels without stringsAsFactors. This must be done when importing data.  
```



# Next, I'll view all entered data regarding species. This will let me know if R views species differently due to typos or differences in capitalization. 

```{r}
unique(Leaves$Species)

# R automatically thinks that differently capitalized or spelled responses are completely different. unique() allows us to view all data in a particular column to ensure that there aren't such data entry errors. 
```

# I can begin fixing this data by combining certain terms which differ by typo of capitalization. This way, I should only have three possible options and my data will be much tidier. 

```{r}
Norway_Maple <- which(Leaves$Species == "Norway maple" | Leaves$Species == "Norway mapel" | Leaves$Species == "Norway Maple")

Leaves$Species[Norway_Maple]<- "Norway Maple"

Red_Maple <- which(Leaves$Species == "red maple" | Leaves$Species == "Red maple" | Leaves$Species == "Red Maple")

Leaves$Species[Red_Maple]<- "Red Maple"

Sugar_Maple <- which(Leaves$Species == "sugar maple" | Leaves$Species == "Sugar maple" | Leaves$Species == "Sugar Maple")

Leaves$Species[Sugar_Maple]<- "Sugar Maple"

# Changes to all three species can be put within this one code block. That makes things much neater than creating three separate blocks. 

# which() combines selected data, allowing one to convert multiple responses into one single response. 

```

# I want to make a dataset with data exclusively from Sugar Maples. I'll use piping to filter data by species, adding this to a new dataset called "Sugar"

```{r}
Sugar<- Leaves %>% filter(Species == "Sugar Maple")

# %>% represents "and then". My code says to take from dataset "Leaves", and then use data corresponding to sugar maples (of the 'Species' column). 
```

# For some reason, I need to correct the column names for the "Sugar" dataset, as I did with the "Leaves" dataset. I'll use the same code. 

```{r}
names(Sugar) <- c("Tree_num", "Species", "Leaf", "DBH_cm", "Petiole_length", "Total_length_cm", "Middle_lobe_length_cm", "Middle_lobe_width_cm", "Person")
```

# Using select, I'll choose which columns I wish to remove from the 'Sugar' dataset. Using a negative sign (-), all columns except those listed (with -) will be displayed in my new dataset, 'Sugar'. 

```{r}
Sugar<- select(Sugar, -Person, -Leaf, -Tree_num)


```

# Now to make a histogram! This is a very ugly histogram, but I'm happy that it worked! Chapter 4 shows how to visualize and display data through graphs.  

```{r}
ggplot(Sugar, aes(x=Petiole_length)) + geom_histogram()

# Assigning X axis Petiole length through ggplot package. This determines what data will be displayed in the histogram. 
```


